H3: Cultural Differences in Symbolization

### 2023-02-06 H3.Rmd
added h3

@@

summary(fit)

fit_results <- apa_print(fit)

@@

>>>>

fit0 <- lm(moral_identity_symbolic ~ 
             mean(x$moral_identity_symbolic)
                    # sex3
                    # + age
                    #  Power.Distance
                    # + Individualism
                    # + Masculinity
                    # + Uncertainty.Avoidance
                    # + Long.Term.Orientation
                    # + Indulgence
                    # + CTL_C
                    # + CTL_DS
                    # + CTL_DG
                 , data = x
            )

summary(fit0)

@@

summary(fit)
anova(fit)
fit_results <- apa_print(fit)

@@

Our third hypothesis predicted relationships between symbolization and specific cultural variables. The variables question are: power distance, individualism, masculinity, uncertainty avoidance, long term orientation, and indulgence, taken from Hofstede (2001), as well as three measures of cultural tightness (domain-specific, domain-general, and a combination index). These variables were inputted at the country level, and as such, we conducted a hierarchical linear regression model to investigate relationship with symbolization. Symbolization was our outcome measure and each cultural variable was included as a predictor in the model.
